Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum

### 2019-05-17 Paper/paper.tex
updated paper.tex and removed previous draft

\author{Franz Martinez}
\email{franzmichel.martinez@ucalgary.ca}
\affiliation{Schulich School of Engineering, University of Calgary, Calgary, Alberta, Canada}
\title{Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells}

@@

\begin{abstract}
Conversion of CO2 to syngas can be achieved in solid oxide electrolysis cells at high temperatures (~1000 K) by using Perovskite-based solid oxides as electrocatalysts. This process is projected to be a viable way of generating fuels by converting, and therefore reducing, CO2 from industrial emissions. However, full understanding of the mechanism involved in CO2 conversion on these electrocatalysts is far from complete. In this work, we perform DFT calculations and reactive molecular dynamics to understand the electronic structure and stability of perovskite-based solid oxides used as electrocatalysts for CO2 conversion. To this end, our study involves firstly, generation of a dataset from DFT calculations, which include optimized geometries, equations of state, surface energies, and slab—CO2 interactions from a set of ABO3-type perovskites. Secondly, we parametrize the reactive force field, ReaxFF, using an annealing Monte Carlo optimizer and a covariance matrix adaptation evolution strategy. Finally, we explore bulk dynamics of the perovskites at high temperature and the time evolution of reactions involving CO2 on the surface of slabs from the perovskites. Of interest, our results demonstrate the modes in which the CO2 is chemisorbed at high temperature; the consequent formation of intermediates; and their role in further conversion of the CO2. This study serves as a base to elucidate the elementary steps involved in the mechanism of CO2 conversion on perovskites at high temperature, which will allow us to understand the most favorable conditions for the reaction to occur and, consequently, provide us of a way to improve the design of perovskite-based solid oxide electrocatalysts.
\end{abstract}

@@

Introduction of Ca and Sr in the A--site of the perovskites favours the formation of oxygen vacancies due to the change in ionic size compared to La and the different charges of these cations. \textbf{cite}
Also, this changes allows for oxygen ionic diffusion through the solid.
The existence of oxygen vacancies in the system needs to be captured by ReaxFF in the form of correctly capturing changes in the chemical environment and in the relative stability of the perovskite unit cell in the absence of one oxygen.
For various perovskites, the oxygen vacancy formation energy is calculated and incorporated into the dataset used to fit ReaxFF.

@@

@@

To exemplify the dynamics on the bulk, diffusion of O$_2^{-2}$ is followed through the perovskite in bulk phase.

Also, to account for the accuracy of the force field, the expansion coefficient is computed for LCFCr and LSFCr.
This value is compared to experimental results ...

@@

>>>>

\author{Franz Martinez}
\email{franzmichel.martinez@ucalgary.ca}
\affiliation{Schulich School of Engineering, University of Calgary, Calgary, Alberta, Canada}
\title{Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum}

@@

\begin{abstract}
\textbf{abstract needs to be updated}

Conversion of CO2 to syngas can be achieved in solid oxide electrolysis cells at high temperatures (~1000 K) by using Perovskite-based solid oxides as electrocatalysts. This process is projected to be a viable way of generating fuels by converting, and therefore reducing, CO2 from industrial emissions. However, full understanding of the mechanism involved in CO2 conversion on these electrocatalysts is far from complete. In this work, we perform DFT calculations and reactive molecular dynamics to understand the electronic structure and stability of perovskite-based solid oxides used as electrocatalysts for CO2 conversion. To this end, our study involves firstly, generation of a dataset from DFT calculations, which include optimized geometries, equations of state, surface energies, and slab—CO2 interactions from a set of ABO3-type perovskites. Secondly, we parametrize the reactive force field, ReaxFF, using an annealing Monte Carlo optimizer and a covariance matrix adaptation evolution strategy. Finally, we explore bulk dynamics of the perovskites at high temperature and the time evolution of reactions involving CO2 on the surface of slabs from the perovskites. Of interest, our results demonstrate the modes in which the CO2 is chemisorbed at high temperature; the consequent formation of intermediates; and their role in further conversion of the CO2. This study serves as a base to elucidate the elementary steps involved in the mechanism of CO2 conversion on perovskites at high temperature, which will allow us to understand the most favorable conditions for the reaction to occur and, consequently, provide us of a way to improve the design of perovskite-based solid oxide electrocatalysts.
\end{abstract}

@@

Introduction of Ca in the A--site of the perovskites favours the formation of oxygen vacancies due to the change in ionic size compared to La and the different charges of these cations. \textbf{cite}
Also, the formation of oxygen vacancies allow for ionic diffusion through the solid, which is an important process present when these solids are used as electrodes in solid oxide fuel or electrolysis cells.
The existence of oxygen vacancies in the system needs to be captured by ReaxFF in the form of correctly capturing changes in the chemical environment and in the relative stability of the solid unit cell in the absence of one oxygen.
For various perovskites, the oxygen vacancy formation energy is calculated and incorporated into the dataset used to fit ReaxFF.

@@

\subsection{Nanoparticle formation of La$_2$O$_3$}

@@

To exemplify the dynamics on the bulk, diffusion of O$_2^{-2}$ is followed through the perovskite in bulk phase.
Also, to account for the accuracy of the force field, the expansion coefficient is computed for LCFCr and this value is compared to experimental results.

@@

\textbf{this may be ommited for a future paper}
